Untitled

### 2024-05-10 code/draft-script.Rmd
run test script for some mcda
reorganize files

fishnet_nowater<- fishnet %>%
  filter(!(uniqueID %in% inWater$uniqueID))
```

@@

# Determine Weight (AHP)

@@

pw_df <- pw_df %>% 
  mutate(unweight = (popden * acc * driving * evse * reg_ev * parking * police * zoning)^0.125) %>% 
  mutate(weighted = unweight / sum(unweight))

>>>>

fishnet_nowater<- fishnet %>%
  filter(!(uniqueID %in% inWater$uniqueID))

@@

@@

pw_df <- pw_df %>% # using the geometric mean method
  mutate(unweight = (popden * acc * driving * evse * reg_ev * parking * police * zoning)^0.125) %>% 
  mutate(weighted = unweight / sum(unweight))
